### 2016-08-25 ms/ms.tex
deleated some sections marilia wrote that did not quite fit

Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. Assembling networks may have higher
rates of species turnover than non-assembling communities because new
species are colonizing and establishing themselves
\citep{mgonigle-2015-x}. Similarly, if pollinators try to maximize
their foraging efficiency based on the species present, interactions
may turnover more quickly than in established communities.

To estimate the temporal turnover of species and interactions, we use
an approach similar to calculating spatial $\beta$-diversity. Instead
of calculating the variation in community composition across sites
within a year, however, we estimated turnover across years at a
site. We first calculated the pairwise dissimilarity of species and
interactions between years within each site using a dissimilarity
estimator that incorporates abundances, while also accounting for
unobserved records \citep{chao-2005-148}. Dissimilarity estimates can
be affected by the total number of species and individuals sampled at
a site \citep[e.g.,][]{ponisio2015farm}. For example, the probability
that two sites do not share any species is higher when there are few
individuals at those sites. Following \cite{ponisio2015farm}, we use
null models that constrained species richness to estimate the
deviation of the observed dissimilarity from that which would be
expected under a random community assembly process. With the corrected
dissimilarity values, we then calculated the multivariate dispersion
of community composition across years \citep{anderson-2011-19}. In
order to test whether assembling hedgerows had more turnover of
species and interactions than non-assembling communities, the species
and interaction temporal turnover estimates were response variables in
a linear mixed models with site type as an explanatory variable along
with random effects for both year and site \citep{lme4, lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., via preferential
attachment), nestedness would increase through time. The connectance
of a network (the proportion of observed out of possible interaction),
is realted to the

The specialization 
The colonization of specialist species or species are beginning to
limit their interaction niche breath as the network assembles would
lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we use
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

We use NODF (weighted or unweighted) to evaluate network nestedness
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and interaction frequency distributions
\citep{Galeano2009}. Lastly, Network specialization was measured using
H2, which estimate the deviation of the observed interaction frequency
between plants and pollinators from a null expectation where all
partners interact in proportion to their abundances
\citep{bluthgen-2006-9}. It ranges from 0 for generalized networks to
1 for specialized networks.

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species loss
and to cascading perturbations. Following \cite{Memmott2004}, we
simulate the extinction of plant species the subsequent extinction
cascades of pollinator species. Because the reproduction of plant
species if facilitated by active restoration efforts, it is unlikely
the extinction of pollinators would affect plant populations in the
hedgerows. However, plants ceasing to bloom, for example in response
to drought, will likely affect the pollinators that depend on
them. Plants species were eliminated based on their degree or
abundance, and the number of pollinators that secondarily went extinct
is calculated. The area below the extinction curve is an estimate of
network robustness \citep{bipartite}.

We also explored how the robustness to cascading perturbations changed
as community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity is related to how
difficult it is to turn a network into completely disconnected groups
of vertexs, or species \citep{costa2007characterization} --- the larger
the algebraic connectivity, the more robust a network is to cascading
perturbations (Gaiarsa et al., submitted), and the harder it is to
break the community into isolated groups of species.

@@

The majority ($76\%$) of the sites tests underwent at least one
significant reorganization of interactions
(Fig.~\ref{fig:changePoints}).  All five of the assembling hedgerows
experienced changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows
experienced significantly more changing points than the non-assembling
networks (difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts that would effect assembling and
non-assembling networks equally.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (estimate of the slope of
closeness variability and persistence $\pm$ standard error of the
estimate, $0.653 \pm 0.225$, $p$-value=$0.009$; slope of closeness
variability and degree, $0.008 \pm 0.002$, $p$-value='$0.002$). Plant
persistence and degree were not significantly related to network
position variability (estimate of the slope of closeness variability
and persistence $\pm$ standard error of the estimate, $-2.063 \pm
3.091$, $p$-value=$0.5$; slope of closeness variability and degree,
$0.0018 \pm 0.002$, $p$-value=$0.3$). The variability of species
network position was not the result of closeness linearly increasing
through time, and, in fact, plant and pollinator closeness decreased
decreased slightly through time (Fig.~S1, estimate of the slope of
closeness through time $\pm$ standard error of the estimate,
pollinators: $-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants
$-0.007 \pm 0.001$, $p$-value=$1.4*10^{-6}$). Through statistically
significant, the slopes are so slight they may not me biologically
significant.

\subsection*{Species and interaction turnover}
The rates of species and interaction temporal turnover was consistent
across assembling hedgerows, non-assembling hedgerows and field
margins, though mature hedgerows has marginally significantly less
species turnover than field margins (estimate $\pm$ standard error of
the estimate of the difference in turnover between field margins and
mature hedgerows, $-0.0498 \pm 0.026$, $p$-value=$0.058$). When
interactions where weighted by their similarity, both assembling and
mature hedgerows had high rates of turnover than field margins
(estimate $\pm$ standard error of the estimate of the difference in
turnover between field margins and assembling hedgerows, $0.115 \pm
0.027$, $p$-value=$0.0002$; field margins and mature hedgerows, $0.082
\pm 0.024$, $p$-value=$0.002$).

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly (estimate of
the slope of nestedness through time $\pm$ standard error of the
estimate, $1.834 \pm 0.6142$, $p$-value=$0.022$, Fig.~
\ref{fig:baci}).  Modularity decreased (Fig.~\ref{fig:baci}), though
the slope was not significantly different from zero (estimate of the
slope of modularity through time $\pm$ standard error of the estimate,
$-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). Specialization remained
relatively constant (estimate of the slope of specialization through time
$\pm$ standard error of the estimate, $0.003$ $\pm$ $0.015$,
$p$-value=$0.827$).

@@

%% marilia: I see where you are going witht he bluthgen reference, but
%% that seemed like something that should be in the intro or
%% methods. Otherwise it is beinging up a new concept we did not
%% previously explain.

@@

% %% vertex/species turnover  - I am not sure I get these results so there might be some nonsense in the below paragraph...
% Given the regional species pool it is possible that specialization
% might be constant because species are not changing their interactions
% through time, and are thus always presenting the same
% degree. Alternatively, there might be a species turnover, but new
% species end up interacting with the same species, and thus, present
% the same degree as the absent species, and the overall specialization
% of the network does not change as community assembles. Thus, secies
% turnover probably happens, but new species might present the same
% role/posotion as the species previous species. We found that vertex
% turnover was higher in assembling and non-assembling hedgerows when
% compared to field margin, but there was no difference between
% them. Thus, perhaps looking only at network level metrics, such as
% nestedness and modularity, when exploring the temporal assembly of
% ecological networks might be misleading, given that we found vertex
% turnover happening at the species level.

>>>>

Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
pollinator species and interaction turnover. Assembling networks may
have higher rates of species turnover than non-assembling communities
because new species are colonizing and establishing themselves
\citep{mgonigle-2015-x}. Similarly, if pollinators try to maximize
their foraging efficiency based on the species present, interactions
may turnover more quickly than in established communities.

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, however, we estimated turnover across years at a site. We
first calculated the pairwise dissimilarity of species and
interactions between years within each site using a dissimilarity
estimator that incorporates abundances, while also accounting for
unobserved records \citep{chao-2005-148}. Dissimilarity estimates can
be affected by the total number of species and individuals sampled at
a site \citep[e.g.,][]{ponisio2015farm}. For example, the probability
that two sites do not share any species is higher when there are few
individuals at those sites. Following \cite{ponisio2015farm}, we use
null models that constrained species richness to estimate the
deviation of the observed dissimilarity from that which would be
expected under a random community assembly process. With the corrected
dissimilarity values, we then calculated the multivariate dispersion
of community composition across years \citep{anderson-2011-19}. In
order to test whether assembling hedgerows had more turnover of
species and interactions than non-assembling communities, the species
and interaction temporal turnover estimates were response variables in
a linear mixed models with site type as an explanatory variable along
with random effects for both year and site \citep{lme4, lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., via preferential
attachment), nestedness would increase through time. The connectance
--- the proportion of observed out of possible interactions --- is
also expected to increase as species preferentially attach to the
core. The network specialization may also change as the community
assembles. If specialist species colonize the network or species begin
to limit their interaction niche breath as the network assembles,
network-level specialization will increase \citep{bluthgen-2006-9}.

To evaluate network nestedness, we used the estimator weighted NODF
citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and interaction frequency distributions
\citep{Galeano2009}. We evaluate network specialization with the
metric H2, which estimate the deviation of the observed interaction
frequency between plants and pollinators from a null expectation where
all partners interact in proportion to their abundances
\citep{bluthgen-2006-9}. It ranges from zero for generalized networks
to one for specialized networks.

To test whether network modularity, nestedness, connectance or
specialization changed linearly with assembly, we use linear mixed
models with the descriptive network metrics as the response variable,
year of assembly as the explanatory variable, and random effects of
site and year. The number of species in a network affects affects the
patterns of interaction possible, so we also examined the change in
plant and pollinator species richness through time. We employ
generalized linear mixed models with Poisson error to model
richness. We scaled explanatory variables.

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species loss
and to cascading perturbations. Following \cite{Memmott2004}, we
simulate plant species extinction and the subsequent extinction
cascades of pollinator species. Because the reproduction of plant
species if facilitated by active restoration efforts, it is unlikely
the extinction of pollinator species would affect plant populations in
the hedgerows. However, plants ceasing to bloom, for example in
response to drought, will likely affect the pollinators that depend on
them. We eliminate plants species based on their degree or abundance,
and the number of pollinators that secondarily went extinct is
calculated. The area below the extinction curve is an estimate of
network robustness \citep{bipartite}.

We also explored how the robustness to cascading perturbations changed
as community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of vertices, or species \citep{costa2007characterization} --- the
larger the algebraic connectivity, the more robust a network is to
cascading perturbations (Gaiarsa et al., submitted), and the harder it
is to break the community into isolated groups of species.

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints}).  All five of
the assembling hedgerows experienced changing points, whereas only
$40\%$ and $81\%$ of non-assembling hedgerows and field margins,
respectively, underwent significant interaction
reorganizations. Assembling hedgerows experienced significantly more
changing points than the non-assembling networks (estimate of the
difference in the odds ratios between assembling and non-assembling
networks, $3.316$, $95\%$ CI $[1.314, 8.572]$, $p$-value=
$0.0117$). Network assembly following restoration is thus punctuated
by more interaction reorganizations than would be expected by
environmental shifts that would effect assembling and non-assembling
networks equally.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (estimate of the slope of
closeness variability and persistence $\pm$ standard error of the
estimate, $0.653 \pm 0.225$, $p$-value=$0.009$; slope of closeness
variability and degree, $0.008 \pm 0.002$, $p$-value='$0.002$). In
addition, plant persistence and degree were not significantly related
to network position variability (estimate of the slope of closeness
variability and persistence $\pm$ standard error of the estimate,
$-2.063 \pm 3.091$, $p$-value=$0.5$; slope of closeness variability
and degree, $0.0018 \pm 0.002$, $p$-value=$0.3$). The variability of
species network position was not the result of closeness linearly
increasing through time, and, in fact, plant and pollinator closeness
decreased slightly through time (Fig.~S1, estimate of the slope of
closeness through time $\pm$ standard error of the estimate,
pollinators: $-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants
$-0.007 \pm 0.001$, $p$-value=$1.4*10^{-6}$). Through statistically
significant, the slopes are so slight they may not me biologically
significant.

\subsection*{Species and interaction turnover}
The rates of species and interaction temporal turnover similar across
assembling hedgerows, non-assembling hedgerows and field margins,
though mature hedgerows has marginally significantly less species
turnover than field margins (estimate $\pm$ standard error of the
estimate of the difference in turnover between field margins and
mature hedgerows, $-0.0498 \pm 0.026$, $p$-value=$0.058$). When
interactions where weighted by their similarity, both assembling and
mature hedgerows had higher rates of turnover than field margins
(estimate $\pm$ standard error of the estimate of the difference in
turnover between field margins and assembling hedgerows, $0.115 \pm
0.027$, $p$-value=$0.0002$; field margins and mature hedgerows, $0.082
\pm 0.024$, $p$-value=$0.002$). The weighted interaction turnover at
assembling hedgerows, however, was not significantly higher than in
non-assembling, mature hedgerows.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly (estimate of
the slope of nestedness through time $\pm$ standard error of the
estimate, $1.834 \pm 0.6142$, $p$-value=$0.022$, Fig.~\ref{fig:baci}).
Modularity decreased (Fig.~\ref{fig:baci}), though the slope was not
significantly different from zero (estimate of the slope of modularity
through time $\pm$ standard error of the estimate, $-0.524$ $\pm$
$0.295$, $p$-value=$0.124$). Connectance decreased as the community
assembled (Fig.~\ref{fig:baci}, estimate of the slope of connectance
through time $\pm$ standard error of the estimate, $-0.0434$ $\pm$
$0.0152$, $p$-value=$0.03$). In contrast, specialization remained
constant (estimate of the slope of specialization through time $\pm$
standard error of the estimate, $0.003$ $\pm$ $0.015$,
$p$-value=$0.827$).

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ standard error of the estimate, pollinators: $0.193$ $\pm$
$0.0729$, $p$-value=$0.008$; plants:$0.212$ $\pm$ $0.0653$,
$p$-value=$0.001$). Pollinator species are colonizing and persisting
at the assembling hedgerows. Though some new plant species may
eshablish themselves in the hedgerows, because the plant species
richness is based on the flowers in the network and not the presence
of a plant at a site, the increase in plant richness is likely due to
plants attracting more visitors as they offer better rewards.

@@

@@
